Fourmile state variables

### 2025-01-31 state_vars.Rmd
look at state vars for dec2024 and started interpret. results

statn <- read_csv('./38HRU_sept2013_updates/catchment_output/Catchment_statnall.csv') %>%
  mutate(date = mdy(time),
         source = 'statn') %>%
  select(-time)

grid <- read_csv('./38HRU_sept2013_updates/catchment_output/Catchment_gridall.csv') %>%
  mutate(date = mdy(time),
         source = 'grid') %>%
  select(-time)

@@

temp <- ggplot(both, 
               aes(date, 
                   tmean,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

@@

ggplot(tmean_avg, aes(x=month, y=mean_tmean,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean tmean (C)')

precip <- ggplot(both, 
               aes(date, 
                   precip,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

@@

ggplot(precip_avg, aes(x=month, y=mean_p,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean precip (mm)')

@@

ggplot(solrad_avg, aes(x=month, y=mean_solrad,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean solrad')

@@

## Interception
- Average interception: grid > statn
- Monthly average: Statn > grid 1:4 and 10:12, grid > statn 5:9
- During the summer rain interception is greater from grid
- In the winter snow interception is greater from statn

@@

ggplot(int_avg, aes(x=month, y=mean_interception,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean interception')

interception <- ggplot(both, 
               aes(date, 
                   interception,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

@@

- Average ET: grid > statn
- Monthly average ET: grid > statn 1:6 and 9:12, statn > grid 7:8

@@

ggplot(et_avg, aes(x=month, y=mean_et,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean ET (mm)')

et <- ggplot(both, 
               aes(date, 
                   actET...21,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y='ET (mm)')

@@

- Grid > Statn
- SWE starts accumulating faster in Sept for statn than grid
- But grid > statn all other months

@@

ggplot(swe_avg, aes(x=month, y=mean_swe,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean SWE (l/day)')

snowTotSWE <- ggplot(both, 
                     aes(date, 
                         snowTotSWE,
                         color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y='SWE (l/day)')

@@

- Statn > grid all months

@@

ggplot(soil_avg, aes(x=month, y=mean_soil,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean soil sat')

soil <- ggplot(both, 
               aes(date, 
                   soilSat,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

@@

- RG1: when there is surface runoff, statn is slightly higher
- Except for September (Sep 2013 flood heavily influences this avg)
- Many of the surface runoff events are happening Mar-May and Jul

@@

ggplot(rd1_avg, aes(x=month, y=mean_rd1,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean surface runoff (l)')

rd1 <- ggplot(both, 
               aes(date, 
                   outRD1,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y='Surface runoff (l)')

@@

- Statn > grid Jan to Apr
- Grid > statn May, Jun, Oct
- Other months are similar

@@

ggplot(rd2_avg, aes(x=month, y=mean_rd2,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean interflow (l)')

rd2 <- ggplot(both, 
               aes(date, 
                   outRD2,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y='Interflow (l)')

@@

- RG1 = shallow groundwater
- RG1: during snowmelt runoff to fall baseflow grid > statn
- RG1: statn > grid during winter

@@

ggplot(gw1_avg, aes(x=month, y=mean_rg1,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean RG1 (unit?)')

gw1 <- ggplot(both, 
               aes(date, 
                   outRG1,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

@@

ggplot(gw2_avg, aes(x=month, y=mean_rg2,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean RG2 (unit?)')

gw2 <- ggplot(both, 
               aes(date, 
                   outRG2,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

@@

@@

ggplot(tmean_avg, aes(x=month, y=mean_tmean,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean tmean (C)')

temp <- ggplot(both_hi, 
               aes(date, 
                   tmean,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

@@

ggplot(precip_avg, aes(x=month, y=mean_p,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean precip (mm)')

precip <- ggplot(both_hi, 
               aes(date, 
                   precip,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

@@

ggplot(solrad_avg, aes(x=month, y=mean_solrad,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean solrad (MJ/m2/day)')

@@

ggplot(int_avg, aes(x=month, y=mean_interception,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean interception')

interception <- ggplot(both_hi, 
               aes(date, 
                   interception,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

@@

ggplot(et_avg, aes(x=month, y=mean_et,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean ET (mm)')

et <- ggplot(both_hi, 
               aes(date, 
                   actET,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y='ET (mm)')

@@

ggplot(swe_avg, aes(x=month, y=mean_swe,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean SWE (l/day)')

snowTotSWE <- ggplot(both_hi, 
                     aes(date, 
                         snowTotSWE,
                         color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y='SWE (l/day)')

@@

ggplot(soil_avg, aes(x=month, y=mean_soil,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean soil sat')

soil <- ggplot(both_hi, 
               aes(date, 
                   soilSat,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

@@

ggplot(rd1_avg, aes(x=month, y=mean_rd1,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean surface runoff (l)')

rd1 <- ggplot(both_hi, 
               aes(date, 
                   outRD1,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y='Surface runoff (l)')

@@

ggplot(rd2_avg, aes(x=month, y=mean_rd2,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean interflow (l)')

rd2 <- ggplot(both_hi, 
               aes(date, 
                   outRD2,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y='Interflow (l)')

@@

ggplot(gw1_avg, aes(x=month, y=mean_rg1,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean RG1 (unit?)')

gw1 <- ggplot(both_hi, 
               aes(date, 
                   outRG1,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

@@

ggplot(gw2_avg, aes(x=month, y=mean_rg2,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean RG2 (unit?)')

gw2 <- ggplot(both_hi, 
               aes(date, 
                   outRG2,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

@@

ggplot(tmean_avg, aes(x=month, y=mean_tmean,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean tmean (C)')

temp <- ggplot(both_lo, 
               aes(date, 
                   tmean,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

@@

ggplot(precip_avg, aes(x=month, y=mean_p,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean precip (mm)')

precip <- ggplot(both_lo, 
               aes(date, 
                   precip,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

@@

ggplot(int_avg, aes(x=month, y=mean_interception,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean interception')

interception <- ggplot(both_lo, 
               aes(date, 
                   interception,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

@@

ggplot(et_avg, aes(x=month, y=mean_et,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean ET (mm)')

et <- ggplot(both_lo, 
               aes(date, 
                   actET,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y='ET (mm)')

@@

ggplot(swe_avg, aes(x=month, y=mean_swe,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean SWE (l/day)')

snowTotSWE <- ggplot(both_lo, 
                     aes(date, 
                         snowTotSWE,
                         color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y='SWE (l/day)')

@@

ggplot(soil_avg, aes(x=month, y=mean_soil,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean soil sat')

soil <- ggplot(both_lo, 
               aes(date, 
                   soilSat,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

@@

ggplot(rd1_avg, aes(x=month, y=mean_rd1,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean surface runoff (l)')

rd1 <- ggplot(both_lo, 
               aes(date, 
                   outRD1,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y='Surface runoff (l)')

@@

ggplot(rd2_avg, aes(x=month, y=mean_rd2,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean interflow (l)')

rd2 <- ggplot(both_lo, 
               aes(date, 
                   outRD2,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y='Interflow (l)')

@@

ggplot(gw1_avg, aes(x=month, y=mean_rg1,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean RG1 (unit?)')

gw1 <- ggplot(both_lo, 
               aes(date, 
                   outRG1,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

@@

ggplot(gw2_avg, aes(x=month, y=mean_rg2,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("orange", "blue")) +
  labs(y= 'Monthly mean RG2 (unit?)')

gw2 <- ggplot(both_lo, 
               aes(date, 
                   outRG2,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("orange", "blue"))

>>>>

statn <- read_csv('./38HRU_dec2024_updates/catchment_output/Catchment_statnall.csv') %>%
  mutate(date = mdy(time),
         source = 'statn') %>%
  select(-time)

grid <- read_csv('./38HRU_dec2024_updates/catchment_output/Catchment_gridall.csv') %>%
  mutate(date = mdy(time),
         source = 'grid') %>%
  select(-time)

@@

temp <- ggplot(both, 
               aes(date, 
                   tmean,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange"))

@@

ggplot(tmean_avg, aes(x=month, y=mean_tmean,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean tmean (C)')

precip <- ggplot(both, 
               aes(date, 
                   precip,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange"))

@@

ggplot(precip_avg, aes(x=month, y=mean_p,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean precip (mm)')

@@

ggplot(solrad_avg, aes(x=month, y=mean_solrad,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean solrad')

@@

- Monthly average: Statn > grid 1:4 and 10:12, grid > statn 5:9
- During the summer rain interception is greater from grid
- In the winter snow interception is greater from statn

@@

ggplot(int_avg, aes(x=month, y=mean_interception,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean interception')

interception <- ggplot(both, 
               aes(date, 
                   interception,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange"))

@@

- Average ET: grid > statn
- Monthly average ET: grid > statn 1:5 and 9:12, statn > grid 6:8

@@

ggplot(et_avg, aes(x=month, y=mean_et,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean ET (mm)')

et <- ggplot(both, 
               aes(date, 
                   actET...21,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y='ET (mm)')

@@

- Despite grid being higher all winter, it melts out faster than statn
- grid generally has higher SWE, but statn starts accumulating earlier & melts slower

@@

ggplot(swe_avg, aes(x=month, y=mean_swe,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean SWE (l/day)')

snowTotSWE <- ggplot(both, 
                     aes(date, 
                         snowTotSWE,
                         color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y='SWE (l/day)')

@@

- 4,5,6,10 statn > SM than grid
- SM higher for statn

@@

ggplot(soil_avg, aes(x=month, y=mean_soil,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean soil sat')

soil <- ggplot(both, 
               aes(date, 
                   soilSat,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange"))

@@

- RG1: very little other than Sept, where grid > statn

@@

ggplot(rd1_avg, aes(x=month, y=mean_rd1,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean surface runoff (l)')

rd1 <- ggplot(both, 
               aes(date, 
                   outRD1,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y='Surface runoff (l)')

@@

- Statn > grid
- very little grid

@@

ggplot(rd2_avg, aes(x=month, y=mean_rd2,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean interflow (l)')

rd2 <- ggplot(both, 
               aes(date, 
                   outRD2,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y='Interflow (l)')

@@

- RG1 = shallow groundwater
- RG1: grid > statn

@@

ggplot(gw1_avg, aes(x=month, y=mean_rg1,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean RG1 (unit?)')

gw1 <- ggplot(both, 
               aes(date, 
                   outRG1,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange"))

@@

ggplot(gw2_avg, aes(x=month, y=mean_rg2,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean RG2 (unit?)')

gw2 <- ggplot(both, 
               aes(date, 
                   outRG2,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange"))

@@

NOTHING BELOW HAS BEEN UPDATED WITH DEC2024 UPDATES

@@

ggplot(tmean_avg, aes(x=month, y=mean_tmean,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean tmean (C)')

temp <- ggplot(both_hi, 
               aes(date, 
                   tmean,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange"))

@@

ggplot(precip_avg, aes(x=month, y=mean_p,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean precip (mm)')

precip <- ggplot(both_hi, 
               aes(date, 
                   precip,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange"))

@@

ggplot(solrad_avg, aes(x=month, y=mean_solrad,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean solrad (MJ/m2/day)')

@@

ggplot(int_avg, aes(x=month, y=mean_interception,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean interception')

interception <- ggplot(both_hi, 
               aes(date, 
                   interception,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange"))

@@

ggplot(et_avg, aes(x=month, y=mean_et,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean ET (mm)')

et <- ggplot(both_hi, 
               aes(date, 
                   actET,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y='ET (mm)')

@@

ggplot(swe_avg, aes(x=month, y=mean_swe,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean SWE (l/day)')

snowTotSWE <- ggplot(both_hi, 
                     aes(date, 
                         snowTotSWE,
                         color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y='SWE (l/day)')

@@

ggplot(soil_avg, aes(x=month, y=mean_soil,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean soil sat')

soil <- ggplot(both_hi, 
               aes(date, 
                   soilSat,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange"))

@@

ggplot(rd1_avg, aes(x=month, y=mean_rd1,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean surface runoff (l)')

rd1 <- ggplot(both_hi, 
               aes(date, 
                   outRD1,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y='Surface runoff (l)')

@@

ggplot(rd2_avg, aes(x=month, y=mean_rd2,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean interflow (l)')

rd2 <- ggplot(both_hi, 
               aes(date, 
                   outRD2,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y='Interflow (l)')

@@

ggplot(gw1_avg, aes(x=month, y=mean_rg1,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean RG1 (unit?)')

gw1 <- ggplot(both_hi, 
               aes(date, 
                   outRG1,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange"))

@@

ggplot(gw2_avg, aes(x=month, y=mean_rg2,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean RG2 (unit?)')

gw2 <- ggplot(both_hi, 
               aes(date, 
                   outRG2,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange"))

@@

ggplot(tmean_avg, aes(x=month, y=mean_tmean,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean tmean (C)')

temp <- ggplot(both_lo, 
               aes(date, 
                   tmean,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange"))

@@

ggplot(precip_avg, aes(x=month, y=mean_p,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean precip (mm)')

precip <- ggplot(both_lo, 
               aes(date, 
                   precip,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange"))

@@

ggplot(int_avg, aes(x=month, y=mean_interception,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean interception')

interception <- ggplot(both_lo, 
               aes(date, 
                   interception,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange"))

@@

ggplot(et_avg, aes(x=month, y=mean_et,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean ET (mm)')

et <- ggplot(both_lo, 
               aes(date, 
                   actET,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y='ET (mm)')

@@

ggplot(swe_avg, aes(x=month, y=mean_swe,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean SWE (l/day)')

snowTotSWE <- ggplot(both_lo, 
                     aes(date, 
                         snowTotSWE,
                         color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y='SWE (l/day)')

@@

ggplot(soil_avg, aes(x=month, y=mean_soil,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean soil sat')

soil <- ggplot(both_lo, 
               aes(date, 
                   soilSat,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange"))

@@

ggplot(rd1_avg, aes(x=month, y=mean_rd1,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean surface runoff (l)')

rd1 <- ggplot(both_lo, 
               aes(date, 
                   outRD1,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y='Surface runoff (l)')

@@

ggplot(rd2_avg, aes(x=month, y=mean_rd2,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean interflow (l)')

rd2 <- ggplot(both_lo, 
               aes(date, 
                   outRD2,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y='Interflow (l)')

@@

ggplot(gw1_avg, aes(x=month, y=mean_rg1,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean RG1 (unit?)')

gw1 <- ggplot(both_lo, 
               aes(date, 
                   outRG1,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange"))

@@

ggplot(gw2_avg, aes(x=month, y=mean_rg2,
                 color=source)) +
  geom_point(size=3) +
  scale_color_manual(values = c("#0047AB", "orange")) +
  labs(y= 'Monthly mean RG2 (unit?)')

gw2 <- ggplot(both_lo, 
               aes(date, 
                   outRG2,
                   color = source)) +
  geom_line() +
  scale_color_manual(values = c("#0047AB", "orange"))
